---
title: "Lead-IQ Data Analysis Report"
author: "Yifan Zhao"
date: "`r Sys.Date()`"
output: 
  pdf_document: default
  
knit: (function(inputFile, encoding) {
      rmarkdown::render(inputFile,
                        encoding=encoding,
                        output_dir="./Reports")})
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Load libraries
library(knitr)
```

In this study, we are interested in the lead-IQ dataset, which is described in detail in the `Background/DataInfo.md` document.

Let's read in the data first, and take a look at the variables in the dataset.

```{r data-loading}
# Read in lead-iq-01.csv
lead_IQ <- read.csv("../DataRaw/lead-iq-01.csv", stringsAsFactors = T)
# Note: Since the report will be generated in the ./Reports folder,
# relative path is used here.

# Print head and tail of the dataset
kable(head(lead_IQ))
kable(tail(lead_IQ))

# Check dimensions
dim(lead_IQ)

# Check variables
summary(lead_IQ)
```


It will be great to show the IQ levels by location status in a box plot.

```{r boxplot}
boxplot(IQ ~ Smelter, data = lead_IQ)
```
As we can see from the figure above, there is an outlier in the Far group. The mean of the IQ is currently `r mean(lead_IQ$IQ)`.

