---
title: "Lead-IQ Data Analysis Report"
author: "Yifan Zhao"
date: "`r Sys.Date()`"
output: 
  pdf_document: default
  
knit: (function(inputFile, encoding) {
      rmarkdown::render(inputFile,
                        encoding=encoding,
                        output_dir="./Reports")})
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Load libraries
library(knitr)
```

# Project Setup
In this study, we are interested in the lead-IQ dataset, which is described in detail in the `Background/DataInfo.md` document.

Let's read in the data first, and take a look at the variables in the dataset.

```{r data-loading}
# Read in lead-iq-01.csv
lead_IQ <- read.csv("../DataRaw/lead-iq-01.csv", stringsAsFactors = T)
# Note: Since the report will be generated in the ./Reports folder,
# relative path is used here.

# Print head and tail of the dataset
kable(head(lead_IQ), row.names = T)
kable(tail(lead_IQ), row.names = T)

# Check dimensions
dim(lead_IQ)

# Check dataset summary
summary(lead_IQ)
```

# Data Correction
After a brief conversation with the primary investigator, it was identified that one individual who had an IQ value of “999” was in fact supposed to have a value of “99”. We need to correct that and save the processed data in the `DataProcessed` folder.

```{r data-correction}
# Change "999" to "99"
lead_IQ$IQ[which(lead_IQ$IQ == 999)] <- 99

# Check the summary of the current dataset
summary(lead_IQ)

# Save the processed data in csv format in the DataProcessed folder
write.csv(lead_IQ, "../DataProcessed/lead-iq-corrected.csv")
```


# Boxplot

It will be great to show the IQ levels by location status in a box plot.

```{r boxplot}
boxplot(IQ ~ Smelter, data = lead_IQ)
```

As we can see from the figure above, the IQ levels in Group Far are generally higher than those in Group Near, but the IQ levels in Group Far have a wider spread than those in Group Near.

# Statistics Summary

- The mean of the IQ is currently `r round(mean(lead_IQ$IQ), digits = 2)`.
- The standard deviation of the IQ is `r round(sd(lead_IQ$IQ), digits = 2)`.
- In Group Near:
    - the mean of the IQ is `r round(mean(lead_IQ$IQ[lead_IQ$Smelter == "Near"]), digits = 2)`;
    - the standard deviation of the IQ is `r round(sd(lead_IQ$IQ[lead_IQ$Smelter == "Near"]), digits = 2)`.
- In Group Far:
    - the mean of the IQ is `r round(mean(lead_IQ$IQ[lead_IQ$Smelter == "Far"]), digits = 2)`;
    - the standard deviation of the IQ is `r round(sd(lead_IQ$IQ[lead_IQ$Smelter == "Far"]), digits = 2)`.

